\documentclass[11pt,a4paper,roman]{moderncv}      
\usepackage[english]{babel}

\moderncvstyle{classic}                            
\moderncvcolor{black}                            

% character encoding
\usepackage[utf8]{inputenc}                     

% adjust the page margins
\usepackage[scale=0.80]{geometry}

% personal data
\name{Muhammad Baihaqi Aulia Asy'ari}{}
\email{baihaqilearning@gmail.com}
\phone[mobile]{+62 82336750134}               
\address{Dinoyo, Malang City, East Java}


\begin{document}

\recipient{To}{Putra Gian Nababan, \\
               Human Resources Business Partner,\\ 
               Jobstreet Surabaya,\\ 
               Putragn@jobstreet.co.id,\\
               Jl. Ngagel Jaya Utara No.33C, Pucang Sewu, Kec. Gubeng, Kota SBY, Jawa Timur 60283}
\date{\today}
\opening{\textbf{Sub: Application for the post of Programmer at PT. Digital Kanva Cerah.}}
\closing{Your Sincerly, \vspace{-1em}}


% \enclosure[Enclosed (Marksheets/Certificates)]{
%               \\ 1. SSLC (Admit/MarkSheet/Certificate)
%                  \hspace{0.0em} 5. GATE (2016) \hspace{2em} 9. Identity-Proof (Voter-Id)\\
%                  2. Diploma (MarkSheet/Certificate)
%                  \hspace{1.8em} 6. SLET (2021) \hspace{1.9em} 10. Resume\\        
%                  3. B.Tech (MarkSheet/Certificate)
%                  \hspace{2.3em} 7. UGC-NET (2022) \hspace{-0.1em} \\
%                  4. M.Tech (MarkSheet/Certificate)
%                  \hspace{2.1em} 8. Caste Certificate \\
%                  }
\makelettertitle



Dear Mr Nababan,
\\
%references such as what and how you got this information
\vspace{1em}
With reference to the subject as cited above, I Baihaqi, would like to apply for the said post. I found the said reference through jobstreet.\\

%narrate why you want to apply
\vspace{1em}
Joining PT. Digital Kanva Cerah as a Developer/Programmer presents an exciting opportunity to contribute to meaningful projects using strong web development skills. Experience includes coursework in Web Development and Advanced Web Development, focusing on HTML, CSS, JavaScript, PHP, SQL, Laravel, MySQL, and Git. Recently, efforts have been directed toward learning the React framework and other JavaScript-based technologies, ensuring up-to-date knowledge in the field. This position aligns perfectly with a commitment to continuous learning and contributing to a forward-thinking team in a fast-evolving tech environment. \\
\vspace{1em}

%add some experiences 
I have some experience as a Fullstack Laravel Developer as furnished below:
\vspace{0.5em}
\begin{itemize}
\item working on a website using Laravel and MVC principle in an RW information system,
\item engineered database using MySQL relational database for the RW information system,
\item colaborate and version control using Git in a Github repository,
\item design the UI for the website using Figma,
\item containerized the tech stack using Docker to ease development and deployment.
\end{itemize}

%conclusion
\vspace{1em}
With hands-on experience as a Fullstack Laravel Developer, including work on a website utilizing Laravel and the MVC principle, engineering a MySQL relational database, and collaborating via Git, this role offers a unique chance to expand on these skills. Proficiency in designing UIs with Figma and containerizing tech stacks using Docker for streamlined development further highlights readiness to contribute to PT. Digital Kanva Cerah's projects. Eager to bring a strong foundation in both back-end and front-end technologies to a dynamic team, with a commitment to continuous learning and innovation. \\

\vspace{1em}
I look forward to an opportunity to serve as a Programmer at PT. Digital Kanva Cerah and be considered for the above-said post.

\vspace{0.5cm}


\makeletterclosing

\end{document}